A Switching Planner for Combined Task and Observation Planning

### 2011-05-01 subarchitectures/planner.sa/trunk/src/latex/AAAI11/aaai11.tex
Middle initial

\special{! /pdfmark where
{pop} {userdict /pdfmark /cleartomark load put} ifelse
[ /Author (Moritz Goebelbecker, Charles O. Gretton, Richard Dearden)
/Title (A Switching Planner for Combined Task and Observation Planning)
/Subject (Proceedings of the Twenty-Fifth Conference on Artificial Intelligence)
/Keywords (planning under uncertainty)
/DOCINFO pdfmark
userdict /pdfmark /cleartomark load put}

>>>>

\special{! /pdfmark where
{pop} {userdict /pdfmark /cleartomark load put} ifelse
[ /Author (Moritz Goebelbecker, Charles Gretton, Richard Dearden)
/Title (A Switching Planner for Combined Task and Observation Planning)
/Subject (Proceedings of the Twenty-Fifth Conference on Artificial Intelligence)
/Keywords (planning under uncertainty)
/DOCINFO pdfmark
userdict /pdfmark /cleartomark load put}
